---
title: "Documentation Presentation"
author: "Sherif Hassan"
date: "January 20, 2018"
output:
  ioslides_presentation:
    logo: logo.jpg
---
#Star Graph Shiny Appllication

#simple star graph demonstration application,that allow you to change star graph size,node color and size as well as edge color and width.

#Input fields avaiable to user when user enter desired value for each variable and changes will automatically appear

#Assignment
####**This Assignment contain of two parts:**     
1. An R Shiny application, complete with input, reactive output, and associated documentation    
2. A Reproducible Pitch Presentation in R Studio Presenter, complete with embedded R code

#R package: igraph
#igraph is used to create the network graph in this app.     
#For more detail about igraph: <http://igraph.org/>


#An example of codes for a full graph

```{r include=FALSE}
library(igraph); library(dplyr);
```

```{r fig.align='center', tidy=TRUE, tidy.opts=list(width.cutoff=55)}
plot(make_star(5) %>% set_edge_attr("color", value = "blue")%>%set_edge_attr("width", value =5)%>%set_vertex_attr("color", value = "green")%>%set_vertex_attr("size", value = 10))
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
